SCPCL000822 - Validation of tumor cells

### 2024-06-12 analyses/cell-type-ewings/cell_type_annotations/SCPCS000490/SCPCL000822_tumor-cell-validation.Rmd
output the updated annotations

```{r}
# export final TSV with annotations 
final_classifications <- classification_df |> 
  dplyr::select(
    cell_barcode = barcodes,
    tumor_cell_classification = combined_cnv_classification
  ) |> 
  unique()

>>>>

```{r}
# export final TSV with annotations 
final_classifications <- new_classification_df |> 
  dplyr::select(
    cell_barcode = barcodes,
    tumor_cell_classification = combined_cnv_classification
  ) |> 
  unique()
